Connectome inferences using partial correlation from imaging calcium signal

### 2014-06-13 article.tex
better notation

 % Three or more authors with the same address:
 % \author{ Antonio Sutera %\and
 %         % \Name{Arnaud Joly} \and
 %         % \Name{Vincent Fran\c{c}ois-Lavet} \and
 %         % \Name{Aaron Qiu} \and
 %         % \Name{Gilles Louppes} \and
 %         % \Name{Damien Ernst} \and
 %         % \name{Pierre Geurts}}
 %         }
\author{Antonio Sutera,
        Arnaud Joly,
        Vincent François-Lavet,
        Aaron Qiu, \\
        Gilles Louppes,
        Damien Ernst,
        Pierre Geurts}

@@

% Introduce notation + goal in mathematical score
% TODO check convention for y_{ij}
The connectomes is represented by a (un)directed graph $G = (V, E)$ comprising
a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
V\right\}$, (un)ordered pair from $V$.
Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
represents a direct link from neuron $i$ to neuron $j$.
The network inference task is set as follows :
\textit{Given the observations $(x^i \in \mathcal{R}^{|V|})_{i=1}^n $
along $n$ periods of time of the $|V|$ neurons, the goal is to infer the
adjacency matrix $A : a_{i,j} = I((i, j) \in E)$ of the graph $G$,
where $I$ is the indicator function.}

>>>>

 % Three or more authors with the same address:
 % \author{ Antonio Sutera %\and
 %         % \Name{Arnaud Joly} \and
 %         % \Name{Vincent Fran\c{c}ois-Lavet} \and
 %         % \Name{Aaron Qiu} \and
 %         % \Name{Gilles Louppe} \and
 %         % \Name{Damien Ernst} \and
 %         % \name{Pierre Geurts}}
 %         }
\author{Antonio Sutera,
        Arnaud Joly,
        Vincent François-Lavet,
        Aaron Qiu, \\
        Gilles Louppe,
        Damien Ernst,
        Pierre Geurts}

@@

% Introduce notation + goal in mathematical score
% TODO check convention for y_{ij}
The connectomes is represented by a (un)directed graph $G = (V, E)$ comprising
a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
V\right\}$, (un)ordered pair from $V$.
Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
represents a direct link from neuron $i$ to neuron $j$.
The network inference task is set as follows :
\textit{Given the observations $(x_t \in \mathcal{R}^{|V|})_{t=1}^T $
along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
adjacency matrix $A : a_{i,j} = I((i, j) \in E)$ of the graph $G$,
where $I$ is the indicator function.}
